Relationships in the extremes and their influence on competition and coexistence

### 2021-08-12 paper/Paper.Rnw
starting G2 resujlts

\section{Results}\label{section:results}
%outline of main resutls
Using our simple two-species lottery model, ATA made a difference for coexistence. Depending on death rate, variance, and difference between species, ATA can either impede or facilitate coexistence. In some cases, the contribution of ATA is the mechanism solely responsible for a positive (or negative) IGR, and the IGR without ATA is negative (or positive). In almost all cases we tested, ATA contributed negatively to coexistence expected for when delta = 1, annual species. Of the annual species cases, only when the species were the same or extremely close to being the same, did ATA have a rescue effect on storage effects and coexistence. For other annual species cases, as the species became moree different, IGR was more negative and the contribution of ATA and storage effect in general became more negligible.

>>>>

\section{Results}\label{section:results}
To explore the relative magnitudes of the contributions to coexistence that come from ATA versus other mechanisms in our simple two-species lottery model (G2), we plotted the decomposing mechanisms against increasing $\sigma$ for various values of $\mu_1 - \mu_2$ and $\delta$ (Figure 4). In almost all cases, aside from when $\delta=1$, the contribution of ATA is less than the contribution of storage effects without ATA, and the former decreases with $\sigma$ while the latter increases with $\sigma$. We see the opposite when $\delta=1$, where the contribution of ATA and greater than the contribution of storage effect without ATA and the trends are reversed. 
%outline of main resutls
Using our simple two-species lottery model, ATA made a difference for coexistence. Depending on death rate, variance, and difference between species, ATA can either impede or facilitate coexistence. In some cases, the contribution of ATA is the mechanism solely responsible for a positive (or negative) IGR, and the IGR without ATA is negative (or positive). In almost all cases we tested, ATA contributed negatively to coexistence expected for when delta = 1, annual species. Of the annual species cases, only when the species were the same or extremely close to being the same, did ATA have a rescue effect on storage effects and coexistence. For other annual species cases, as the species became moree different, IGR was more negative and the contribution of ATA and storage effect in general became more negligible.
